Paper 1

### 2018-09-15 paper1.tex
Finished question 2 and added started n-ary

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% DISCUSS THE ABOVE CLAIMED THEOREM AND PROOF.
% YOU SHOULD WRITE TWO OR THREE PARAGRAPHS TO DISCUSS THE ISSUES BELOW.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
The theorem is false, because there is a counter example to the theorem. Take $x=2$, and $m=n=2$.
Then if we assume that the theorem is true, we can write $$2=\left(\frac{a}{b}\right)^2.$$
Because $a,b$ are positive, 
	$$\sqrt{2}=\frac{a}{b}.$$
However, this is impossible because $\dfrac{a}{b}$ is a rational number, but $\sqrt{2}$ is not.
So the theorem is disproved with a counterexample.

Secondly, the proof is incorrect because it only is able to prove .... 
If we were to draw a diagram which illustrates the induction of the proof, it would look like this:

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Look for a similar theorem in the Proofs So Far.
	% You will have to extend the argument a bit.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% DISCUSS THE ABOVE CLAIMED THEOREM AND PROOF.
% YOU SHOULD WRITE TWO OR THREE PARAGRAPHS TO DISCUSS THE ISSUES BELOW.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
The theorem is false, because there is a counter example to the theorem. Take $x=2$, and $m=n=2$.
Then if we assume that the theorem is true, we can write, with naturals $a,b$ $$2=\left(\frac{a}{b}\right)^2.$$
Because $a,b$ are positive, 
	$$\sqrt{2}=\frac{a}{b}.$$
However, this is impossible because $\dfrac{a}{b}$ is a rational number, but $\sqrt{2}$ is not.
So there is a contradiction, and the theorem is disproved.

So, the proof does not prove the theorem, but it was able to prove, through induction, that $x=a^m/b$ works and $x=a/b^n$ works independently. 
However, it does not follow that for every $m,n\in\NN$, and for every positive $x\in\QQ$, there exist $a,b\in\NN$ such that $x = a^m / b^n$.

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Look for a similar theorem in the Proofs So Far.
	% You will have to extend the argument a bit.
	%
	Let $P(x)$ be the statement of the theorem. $P(0)$ is trivially true because if we write, 
	$$
		0 = \sum_{j=0}^\infty a_j n^j,
	$$
	the certainly exists an $n$-ary sequence $(a_j)_{j\in\NN^0}$ that is just the infinite sequence with all 0s. This sequence would be $n$-ary for every $n$ because for the the smallest $n$, which is 2, $\{0\}\subset\{0,1\}$.

	Now, let $x$ be a natural number such that $x>0$, and suppose that $P(k)$ is true for all integer $k$ such that $0\leq k\leq x$. Now, we want to show that $P(x+1)$ is also true.

	If $x+1$ is divisible by $n$, then $\frac{x+1}{n}\in \NNzero$ and $0\leq\frac{x+1}{n}\leq x$. Since we know that $P(k)$ is true, we know that there exists an $n$-ary sequence such that 
	$$
		\frac{x+1}{n} = \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^j
	$$
	where $a_{\frac{x+1}{n},j}$ is the $j$th term in the sequence $a_{\frac{x+1}{n}}$
	Manipulating this equation yields, 
	\begin{align*}
		x+1 &= \sum_{j=0}^\infty a_{\frac{x+1}{n},j} n^{j+1} \\
		x+1 &= \sum_{j=1}^\infty a_{\frac{x+1}{n},j-1} n^{j}.
	\end{align*}
	Now let us define a new sequence $a_{x+1}$ such that $a_{x+1,j} = a_{\frac{x+1}{n},j-1}$
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
